### 2016-06-27 publications/Journal/abstract.tex
* fixed typo in abstract * some very minute changes.

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11, but based on PythonPDEVS, which supports both conservative and optimistic synchronization protocols with the capability to switch during simulation between those protocols.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol and demonstrate the inlfuence model allocation and uncertainty has on this choice. 
Performance results are compared to adevs, in terms of CPU time and memory usage.

>>>>

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11, but based on PythonPDEVS, which supports both conservative and optimistic synchronization protocols with the capability to switch during simulation between those protocols.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol and demonstrate the influence model allocation and uncertainty has on this choice. 
Performance results are compared to adevs, in terms of CPU time and memory usage.

### 2016-06-27 publications/Journal/parallel-performance.tex
* fixed typo in abstract * some very minute changes.

In a sequential simulation kernel no allocated event will persist beyond a single time advance,  this enables the use of an arena-style allocator. Conservative and optimistic simulation need to use generic pool allocators since events are shared across kernels and thus have a different lifetime. \\

@@

Dxex uses Boost Pool\cite{boostpool} allocators in parallel simulation kernels, and can use arena-style allocators for sequential simulation.

>>>>

In a sequential simulation kernel no allocated event will persist beyond a single time advance, allowing the use of an arena-style allocator. Conservative and optimistic simulation need to use generic pool allocators since events are shared across kernels and thus have a different lifetime. \\

@@

Dxex uses Boost Pool\cite{boostpool} allocators in parallel simulation kernels and arena-style allocators for sequential simulation.
